\textit{Supplementary materials for}: Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-20 paper/main.tex
addressed PFC comments
in addition to (mostly) text changes, i've also changed figure S9 to show spearman correlation coefficients in the lower triangle and p-values in the upper triangle, using two different colormaps.

\begin{document}
\maketitle

@@

The stimuli in our paradigm were 256 English words selected in a previous
study~\citep{ZimaEtal18}. All words referred to concrete nouns and were
chosen from 15 unique semantic categories: body parts, building-related,
cities, clothing, countries, flowers, fruits, insects, instruments,
kitchen-related, mammals, (US) states, tools, trees, and vegetables. We also
tagged each word according to the approximate size of the object it
referred to. Words were labeled as ``small'' if the referent object was
likely able to ``fit in a standard shoebox'' or ``large'' if the object was
larger than a shoebox. Most semantic categories comprised words that reflected
both ``small'' and ``large'' object sizes, but several included only one or the
other (e.g., all countries, US states, and cities are larger than a shoebox;
mean number of different sizes per category: 1.33; standard deviation: 0.49).
The number of words in each semantic category also varied from 12--28 (mean
number of words per category: 17.07; standard deviation: 4.65).
We also identified lexicographic features for each word, including its
first letter and length (i.e., number of letters). Across all categories, all
possible first letters were represented except for `Q' (average number of
unique first letters per category: 11; standard deviation: 2 letters). Word
lengths ranged from 3--12 letters (average: 6.17 letters; standard deviation:
2.06 letters).

@@

To select a random font color for each word, we drew three integers uniformly
and at random from the interval $\left[0,~254\right]$, corresponding to the red
(r), green (g), and blue (b) color channels for that word. To assign random
presentation locations to each word, we selected two floating point numbers
uniformly and at random (one for the word's horizontal $x$-coordinate and the
other for its vertical $y$-coordinate). The bounds of these coordinates were
selected to cover the entire visible area of the display without cutting off
any part of the words. The words were shown on 27-in (diagonal) Retina 5K iMac
displays (resolution: 5120 $\times$ 2880 pixels).

Most of the experimental manipulations we carried out entailed presenting or
sorting the presented words differently on the first eight lists participants
studied (which we call ``\textit{early}'' lists) versus on the final eight lists
they studied (``\textit{late}'' lists). Since every participant studied exactly 16
lists, every list was either ``early'' or ``late'' depending on its order in
the list study sequence.

@@

Our experimental paradigm incorporates the Google Cloud Speech API
speech-to-text engine~\citep{HalpEtal16} to automatically transcribe
participants' verbal recalls into text. This allows recalls to be transcribed
in real time---a distinguishing feature of the experiment; in typical verbal
recall experiments, the audio data must be parsed and transcribed manually. In
prior work, we used a similar experimental setup (equivalent to the ``reduced''
condition in the present study) to verify that the automatically transcribed
recalls were sufficiently close to human-transcribed recalls to yield reliable
data~\citep{ZimaEtal18}. This real-time speech processing component of the
paradigm plays an important role in the ``adaptive'' condition of the
experiment, as described below.

@@

\paragraph{Constructing feature-sorted lists.} Given a list of words, a
relevant feature, and each word's value(s) for that feature, we developed a
stochastic algorithm for (noisily) sorting the words. The stochastic aspect of
our sorting procedure enabled us to obtain unique orderings for each
participant. First, we choose a word uniformly and at random from the set of
words on the to-be-presented list. Second, we compute the distances between the
chosen word's feature(s) and the corresponding feature(s) of all
yet-to-be-presented words. Third, we convert these distances (between the
previously presented word's feature values, $a$, and the candidate word's
feature values, $b$) to similarity scores:

\begin{equation}
 \mathrm{similarity}(a, b) = \exp\{-\tau \cdot
\mathrm{distance}(a, b)\}, \label{eqn:similarity}
\end{equation}
where $\tau = 1$ in our implementation. We note that increasing the value of
$\tau$ would amplify the influence of similarity on order, and decreasing the
value of $\tau$ would diminish the influence of similarity on order. Also note
that this approach requires $\tau > 0$. Finally, we compute a set of
normalized similarity values by dividing the similarities by their sum:

\begin{equation}
\mathrm{similarity}_{\mathrm{normalized}}(a, b) = \frac{\mathrm{similarity}(a,
b)}{\sum_{i=1}^n \mathrm{similarity}(a, i)},
\end{equation}
where in the denominator, $i$ takes on the feature value of each of the $n$
to-be-presented words. The resulting set of normalized similarity scores sums
to 1.

@@

Following some of our prior work~\citep{FitzEtal23, HeusEtal18a, HeusEtal21, MannEtal22},
we used low-dimensional embeddings to help visualize how participants' memory
fingerprints change across lists
(Figs.~\ref{fig:fingerprint-trajectories}A,~\fingerprintTrajectoryRandom A). To
compute a shared embedding space across participants and experimental
conditions, we concatenated the full set of across-participant average
fingerprints (for all lists and experimental conditions) to create a large
matrix with number-of-lists (16) $\times$ number-of-conditions (10, including
the adaptive condition) rows and seven columns (one for each feature clustering
score, plus an additional temporal clustering score column). We used principal
components analysis to project the seven-dimensional observations into a
two-dimensional space (using the two principal components that explained the
most variance in the data). For two visualizations
(Figs.~\ref{fig:fingerprint-trajectories}B,~\fingerprintTrajectoryRandom B),
we computed an additional set of two-dimensional embeddings for the
\textit{average} fingerprints across lists within a given list grouping (i.e.,
early or late). For those visualizations, we averaged across the rows (for each
condition and group of lists) in the combined fingerprint matrix prior to
projecting it into the shared two-dimensional space. This yielded a single
two-dimensional coordinate for each \textit{list group} (in each condition),
rather than for each individual list. We used these embeddings solely for
visualization; all statistical tests were carried out in the original
(seven-dimensional) feature spaces.

@@

Serial position curves~\citep{Murd62a} reflect the proportion of participants
who remember each item as a function of the items' serial positions during
encoding. For each participant, we initialized a number-of-lists (16) by
number-of-words-per-list (16) matrix of 0s. Then, for each correct recall, we
identified the presentation position of the word and entered a 1 into that
position (row: list; column: presentation position) in the matrix. This
resulted in a matrix whose entries indicated whether or not the words presented
at each position, on each list, were recalled by the participant (depending on
whether the corresponding entires were set to 1 or 0). Finally, we averaged
over the rows of the matrix to yield a 1 by 16 array representing the
proportion of words at each position that the participant remembered.

@@

\subsection*{Data and code availability}

@@

A core assumption of our approach is that each participant organizes their
memories in a unique way. We defined each participant's \textit{memory
fingerprint} as the set of their permutation-corrected clustering scores across
all dimensions we tracked in our study, including their six feature-based
clustering scores (category, size, length, first letter, color, and location)
and their temporal clustering score. Conceptually, a participant's memory
fingerprint describes their tendency to order, in their recall sequences (and
presumably, organize in memory), the studied words along each dimension. If
these memory fingerprints are truly unique to each participant, then we would
expect that the estimated fingerprints computed for a given participant, on
different lists, should be more similar than the estimated fingerprints
computed for different participants. We reasoned that the feature-rich
condition would provide the best opportunity to test this assumption, since the
clustering scores would not be potentially confounded by order manipulations.
To test our ``unique memory fingerprint'' assumption, we compared the
similarity (correlation) between the fingerprint from a single list (from one
participant) and (a) the average fingerprint from all other lists from the same
participant versus (b) the average fingerprint from each other participant
(across all of their lists). Repeating this procedure for all lists and
participants, we found that participants' fingerprints for a held-out list were
reliably more similar to their fingerprints for other lists than they were to
 other participants' fingerprints ($t(70280) = 5.077,~p < 0.001,~d =
0.162,~\mathrm{CI} = [3.086,~6.895]$). This suggests that participants'
fingerprints are relatively stable across lists, and that each participant's fingerprint
is unique to them.

@@

\caption{\textbf{Recall dynamics in feature-rich free recall (order
manipulation conditions).} \textbf{A.} Behavioral plots. \textbf{Left panels.}
The probabilities of initiating recall with each word are plotted as a function
of presentation position. \textbf{Middle panels.} The conditional probabilities
of recalling each word are plotted as a function of the relative position (lag)
to the word recalled just-prior. \textbf{Right panels.} The overall
probabilities of recalling each word are plotted as a function of presentation
position. \textbf{All panels.} Error ribbons denote bootstrap-estimated 95\%
confidence intervals (calculated across participants). Top panels display the
recall dynamics for early (order manipulation) lists in each condition (color).
Bottom panels display the recall dynamics for late (randomly ordered) lists.
See Figures~\dynamicsRandom~and~\dynamicsAdaptive~for analogous plots for the
random and adaptive conditions. \textbf{B.} Distances between successively
presented words ($z$-scored within condition) computed based on each condition's
feature of focus, and plotted as a function of presentation position. See
\textit{Defining feature-based distances} for additional information. \textbf{C.} Proportion of
event boundaries (see \textit{Identifying event boundaries}) for each
condition's feature of focus, plotted as a function of presentation position.}

@@

    \caption{\textbf{Memory fingerprint dynamics (order manipulation
    conditions).} \textbf{A.} Each column (and color) reflects an experimental
    condition. In the top panels, each marker displays a 2D projection of the
    (across-participant) average memory fingerprint for a single list. Order
    manipulation (early) lists are denoted by circles and randomly ordered
    (late) lists are denoted by stars. All of the fingerprints (across all
    conditions and lists) are projected into a common space. The bar plots in
    the bottom panels display the Euclidean distances between each per-list memory
    fingerprint and the average fingerprint across all prior lists, for each
    condition. Error bars denote bootstrap-estimated 95\% confidence intervals.
    The dotted vertical lines denote the boundaries between early and late
    lists. \textbf{B.} In this panel, the fingerprints for early (circle) and
    late (star) lists are averaged across lists and participants before
    projecting the fingerprints into a (new) 2D space. See
    Figure~\fingerprintTrajectoryRandom~for analogous plots for the random
    conditions. } \label{fig:fingerprint-trajectories}

@@

A large number of prior studies have compared participants' memories for
categorized word lists that are presented in blocked versus random orders. In
``blocked'' lists, all of the words from a given semantic category (e.g.,
animals) are presented consecutively, whereas in ``random'' lists, the words
from different categories are intermixed. Most of these studies report that
participants tend to better remember blocked (versus random)
lists~\citep{CofeEtal66, DAgo69, Dall64, Shap70, ShapPalm70, Kint70,
BoweEtal68, BoweEtal69, LuekEtal71, Puff74}. Other studies suggest that these order
effects may also be modulated by factors like list length and the numbers of
exemplars in each category~\citep[e.g.,][]{BorgMang72}.

@@

Conceptualization: JRM and ACH. Methodology: JRM and ACH. Software: JRM, PCF,
CEF, and ACH. Analysis: JRM, PCF, and ACH. Data collection: ECW, PCF, MRL, AMF,
BJB, DR, and CEF. Data curation and management: ECW, PCF, MRL, and ACH. Writing
(original draft): JRM. Writing (review and editing): ECW, PCF, MRL, AMF, BJB,
DR, CEF, and ACH. Supervision: JRM and ACH. Project administration: ECW and
PCF. Funding acquisition: JRM.

>>>>

\begin{document}
\maketitle
\thispagestyle{empty}

@@

The stimuli in our paradigm were 256 English words selected in a previous
study~\citep{ZimaEtal18}. All words referred to concrete nouns and were chosen
from 15 unique semantic categories: body parts, building-related, cities,
clothing, countries, flowers, fruits, insects, instruments, kitchen-related,
mammals, (US) states, tools, trees, and vegetables. We also tagged each word
according to the approximate size of the object it referred to. Words were
labeled as ``small'' if the referent object was likely able to ``fit in a
standard shoebox'' or ``large'' if the object was larger than a shoebox. Most
semantic categories comprised words that reflected both ``small'' and ``large''
object sizes, but several included only one or the other (e.g., all countries,
US states, and cities are larger than a shoebox; mean number of different sizes
per category: 1.33; standard deviation: 0.49). The number of words in each
semantic category also varied from 12--28 (mean number of words per category:
17.07; standard deviation: 4.65). We also identified lexicographic features for
each word, including its first letter and length (i.e., number of letters).
Across all categories, all possible first letters were represented except for
`Q' (average number of unique first letters per category: 11.00; standard
deviation: 2.00 letters). Word lengths ranged from 3--12 letters (average: 6.17
letters; standard deviation: 2.06 letters).

@@

To select a random font color for each word, we drew three integers uniformly
and at random from the interval $\left[0,~254\right]$, corresponding to the red
(r), green (g), and blue (b) color channels for that word. To assign random
presentation locations to each word, we selected two floating point numbers
uniformly and at random (one for the word's horizontal $x$-coordinate and the
other for its vertical $y$-coordinate). The bounds of these coordinates were
selected to cover the entire visible area of the display without cutting off
any part of the words. The words were shown on 27-in (diagonal) Retina 5K iMac
displays (resolution: 5120 by 2880 pixels).

Most of the experimental manipulations we carried out entailed presenting or
sorting the presented words differently on the first eight lists participants
studied (which we call ``\textit{early}'' lists) versus on the final eight
lists they studied (``\textit{late}'' lists). Since every participant studied
exactly 16 lists, every list was either ``early'' or ``late'' depending on its
order in the list study sequence. (In other words, the ``early'' and ``late''
labels capture all of the lists participants studied.)

@@

Our experimental paradigm incorporates the Google Cloud Speech-to-Text
engine~\citep{HalpEtal16} to automatically transcribe participants' verbal
recalls into text. This allows recalls to be transcribed in real time---a
distinguishing feature of the experiment; in typical verbal recall experiments,
the audio data must be parsed and transcribed manually. In prior work, we used
a similar experimental setup (equivalent to the ``reduced'' condition in the
present study) to verify that the automatically transcribed recalls were
sufficiently close to human-transcribed recalls to yield reliable
data~\citep{ZimaEtal18}. This real-time speech processing component of the
paradigm plays an important role in the ``adaptive'' condition of the
experiment, as described below.

@@

\paragraph{Constructing feature-sorted lists.} Given a list of words, a
relevant feature, and each word's value(s) for that feature, we developed a
stochastic algorithm for (noisily) sorting the words. The stochastic aspect of
our sorting procedure enabled us to obtain unique orderings for each
participant. First, we choose a word uniformly and at random from the set of
words on the to-be-presented list. Second, we compute the distances between the
chosen word's feature(s) value(s) and the corresponding feature(s) value(s) of
all yet-to-be-presented words. Third, we convert these distances (between the
previously presented word's feature values, $a$, and each of the $W$
yet-to-be-presented candidate words' feature values, $b_{i \in 1...W}$) to
similarity scores:

\begin{equation}
 \mathrm{similarity}(a, b_i) = \exp\{-\tau \cdot
\mathrm{distance}(a, b_i)\}, \label{eqn:similarity}
\end{equation}
where $\tau = 1$ in our implementation. We note that increasing the value of
$\tau$ would amplify the influence of similarity on order, and decreasing the
value of $\tau$ would diminish the influence of similarity on order. Also note
that this approach requires $\tau > 0$. Finally, we compute a set of
normalized similarity values by dividing the similarities by their sum:

\begin{equation}
\mathrm{similarity}_{\mathrm{normalized}}(a, b_i) = \frac{\mathrm{similarity}(a,
b)}{\sum_{j=1}^W \mathrm{similarity}(a, b_j)},
\end{equation}
where in the denominator, $b_j$ takes on the feature value of each of the $W$
to-be-presented words. The resulting set of normalized similarity scores sums
to 1.

@@

Following some of our prior work~\citep{FitzEtal23, HeusEtal18a, HeusEtal21,
MannEtal22}, we used low-dimensional embeddings to help visualize how
participants' memory fingerprints change across lists
(Figs.~\ref{fig:fingerprint-trajectories}A,~\fingerprintTrajectoryRandom A). To
compute a shared embedding space across participants and experimental
conditions, we concatenated the full set of across-participant average
fingerprints (for all lists and experimental conditions) to create a large
matrix with number-of-lists (16) by number-of-conditions (10, including the
adaptive condition) rows and seven columns (one for each feature clustering
score, plus an additional temporal clustering score column). We used principal
components analysis to project the seven-dimensional observations into a
two-dimensional space (using the two principal components that explained the
most variance in the data). For two visualizations
(Figs.~\ref{fig:fingerprint-trajectories}B,~\fingerprintTrajectoryRandom B), we
computed an additional set of two-dimensional embeddings for the
\textit{average} fingerprints across lists within a given list grouping (i.e.,
early or late). For those visualizations, we averaged across the rows (for each
condition and group of lists) in the combined fingerprint matrix prior to
projecting it into the shared two-dimensional space. This yielded a single
two-dimensional coordinate for each \textit{list group} (in each condition),
rather than for each individual list. We used these embeddings solely for
visualization; all statistical tests were carried out in the original
(seven-dimensional) feature spaces.

@@

Serial position curves~\citep{Murd62a} reflect the proportion of participants
who remember each item as a function of the items' serial positions during
encoding. For each participant, we initialized a number-of-lists (16) by
number-of-words-per-list (16) matrix of 0s. Then, for each correct recall, we
identified the presentation position of the word and entered a 1 into that
position (row: list; column: presentation position) in the matrix. This
resulted in a matrix whose entries indicated whether or not the words presented
at each position, on each list, were recalled by the participant (depending on
whether the corresponding entires were set to 1 or 0). Finally, we averaged
over the rows of the matrix to yield a 1 by 16 array representing the
proportion of words at each position that the participants remembered.

@@

\subsection*{Transparency and openness}

@@

A core assumption of our approach is that each participant organizes their
memories in a unique way. We defined each participant's \textit{memory
fingerprint} as the set of their permutation-corrected clustering scores across
all dimensions we tracked in our study, including their six feature-based
clustering scores (category, size, length, first letter, color, and location)
and their temporal clustering score. Conceptually, a participant's memory
fingerprint describes their tendency to order, in their recall sequences (and
presumably, organize in memory), the studied words along each dimension. If
these memory fingerprints are truly unique to each participant, then we would
expect that the estimated fingerprints computed for a given participant, on
different lists, should be more similar than the estimated fingerprints
computed for different participants. We reasoned that the feature-rich
condition would provide the best opportunity to test this assumption, since the
clustering scores would not be potentially confounded by order manipulations.
To test our ``unique memory fingerprint'' assumption, we compared the
similarity (correlation) between the fingerprint from a single list (from one
participant) and (a) the average fingerprint from all other lists from the same
participant versus (b) the average fingerprint from each other participant
(across all of their lists). Repeating this procedure for all lists and
participants, we found that participants' fingerprints for a held-out list were
reliably more similar to their fingerprints for other lists than they were to
other participants' fingerprints ($t(70280) = 5.077,~p < 0.001,~d =
0.162,~\mathrm{CI} = [3.086,~6.895]$). That within-participant fingerprint
similarity was greater than between-participant fingerprint similarity suggests
that participants' memory fingerprints are relatively stable across lists, and
that each participant's fingerprint is unique to them.

@@

\caption{\textbf{Recall dynamics in feature-rich free recall (order
manipulation conditions).} \textbf{A.} Behavioral plots. \textbf{Left panels.}
The probabilities of initiating recall with each word are plotted as a function
of presentation position. \textbf{Middle panels.} The conditional probabilities
of recalling each word are plotted as a function of the relative position (lag)
to the word recalled just-prior. \textbf{Right panels.} The overall
probabilities of recalling each word are plotted as a function of presentation
position. Top panels display the recall dynamics for early (order manipulation)
lists in each condition (color). Bottom panels display the recall dynamics for
late (randomly ordered) lists. See
Figures~\dynamicsRandom~and~\dynamicsAdaptive~for analogous plots for the
random and adaptive conditions. \textbf{B.} Distances between successively
presented words ($z$-scored within condition) computed based on each
condition's feature of focus, and plotted as a function of presentation
position. See \textit{Defining feature-based distances} for additional
information. \textbf{C.} Proportion of event boundaries (see
\textit{Identifying event boundaries}) for each condition's feature of focus,
plotted as a function of presentation position. \textbf{All panels.} Error
ribbons denote bootstrap-estimated 95\% confidence intervals (calculated across
participants in Panel A, and across lists in Panels B and C).}

@@

    \caption{\textbf{Memory fingerprint dynamics (order manipulation
    conditions).} \textbf{A.} Each column (and color) reflects an experimental
    condition. In the top panels, each marker displays a 2D projection of the
    (across-participant) average memory fingerprint for a single list. Lines
    connect successive lists. Order manipulation (early) lists are denoted by
    circles and randomly ordered (late) lists are denoted by stars. All of the
    fingerprints (across all conditions and lists) are projected into a common
    space. The bar plots in the bottom panels display the Euclidean distances
    between each per-list memory fingerprint and the average fingerprint across
    all prior lists, for each condition. Error bars denote bootstrap-estimated
    95\% confidence intervals. The dotted vertical lines denote the boundaries
    between early and late lists. \textbf{B.} In this panel, the fingerprints
    for early (circle) and late (star) lists are averaged across lists and
    participants before projecting the fingerprints into a (new) 2D space. See
    Figure~\fingerprintTrajectoryRandom~for analogous plots for the random
    conditions. } \label{fig:fingerprint-trajectories}

@@

A large number of prior studies have compared participants' memories for
categorized word lists that are presented in blocked versus random orders. In
``blocked'' lists, all of the words from a given semantic category (e.g.,
animals) are presented consecutively, whereas in ``random'' lists, the words
from different categories are intermixed. Most of these studies report that
participants tend to better remember blocked (versus random)
lists~\citep{CofeEtal66, DAgo69, Dall64, Shap70, ShapPale70, Kint70,
BoweEtal69, LuekEtal71, Puff74}. Other studies suggest that these order
effects may also be modulated by factors like list length and the numbers of
exemplars in each category~\citep[e.g.,][]{BorgMang72}.

@@

Conceptualization: JRM and ACH. Data curation: JRM, PCF, ACH. Formal analysis:
JRM, PCF, and ACH. Funding acquisition: JRM. Investigation: ECW, PCF, MRL, AMF,
BJB, DR, CEF, and ACH. Methodology: JRM and ACH. Project administration: ECW
and PCF. Resources: JRM. Software: JRM, PCF, CEF, and ACH. Supervision: JRM and
ACH. Validation: JRM, PCF, and ACH. Writing (original draft): JRM. Writing
(review and editing): ECW, PCF, MRL, AMF, BJB, DR, CEF, and ACH.

### 2023-11-20 paper/supplement.tex
addressed PFC comments
in addition to (mostly) text changes, i've also changed figure S9 to show spearman correlation coefficients in the lower triangle and p-values in the upper triangle, using two different colormaps.

\renewcommand{\figurename}{Supplementary Figure}

@@

    \caption{\textbf{Memory fingerprint dynamics (random conditions).}
    \textbf{A.} Each column (and color) reflects an experimental condition. In
    the top panels, each marker displays a 2D projection of the
    (across-participant) average memory fingerprint for a single list. Early lists
    are denoted by circles and late lists are denoted by stars. All of the
    fingerprints (across all conditions and lists) are projected into a common
    space. The bar plots in the bottom panels display the Euclidean distances
    between each per-list memory fingerprint and the average fingerprint across all
    prior lists, for each condition. Error bars denote bootstrap-estimated 95\%
    confidence intervals. The dotted vertical lines denote the boundaries
    between early and late lists. \textbf{B.} In this panel, the fingerprints
    for early (circle) and late (star) lists are averaged across lists and
    participants before projecting the fingerprints into a (new) 2D space.}
    \label{fig:fingerprint-trajectories-random}

@@

        \caption{\textbf{Correlations between features.} Within each list, for each participant, we
        computed the set of distances between each pair of words, along each feature dimension.  We
        then combined these pairwise distances across all lists and participants, and computed the
        Spearman correlation between the distances for each pair of feature dimensions.  The correlation
        coefficients are displayed in their corresponding cells of the heatmap.} \label{fig:feature-correlations}

>>>>

%\renewcommand{\figurename}{Supplementary Figure}

@@

    \caption{\textbf{Memory fingerprint dynamics (random conditions).}
    \textbf{A.} Each column (and color) reflects an experimental condition. In
    the top panels, each marker displays a 2D projection of the
    (across-participant) average memory fingerprint for a single list. Early
    lists are denoted by circles and late lists are denoted by stars. Lines
    connect successive lists. All of the fingerprints (across all conditions
    and lists) are projected into a common space. The bar plots in the bottom
    panels display the Euclidean distances between each per-list memory
    fingerprint and the average fingerprint across all prior lists, for each
    condition. Error bars denote bootstrap-estimated 95\% confidence intervals.
    The dotted vertical lines denote the boundaries between early and late
    lists. \textbf{B.} In this panel, the fingerprints for early (circle) and
    late (star) lists are averaged across lists and participants before
    projecting the fingerprints into a (new) 2D space.}
    \label{fig:fingerprint-trajectories-random}

@@

        \caption{\textbf{Correlations between features.} Within each list, for
        each participant, we computed the set of distances between each pair of
        words, along each feature dimension. We then combined these pairwise
        distances across all lists and participants, and computed the Spearman
        correlation coefficient ($\rho$) between the distances for each pair of
        feature dimensions. The correlation coefficients are displayed in their
        corresponding cells of the heatmap in the lower triangle, and the
        corresponding $p$-values are displayed in the upper triangle.}
        \label{fig:feature-correlations}
